General analysis notebook for `forward` budget models.

### 2018-02-26 voltagebudget/analysis/ranked_analysis.Rmd
Improved rank vis

```{r, message=FALSE}
name <- "../data/exp18_d-2e-3_f12_r50.csv"
results <- read_csv(paste(name, sep=""))
```

```{r, fig.width=2.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=delta_variances)) +
  geom_histogram(bins=20) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  ggplot(aes(x=errors)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  ggplot(aes(x=V_osc)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  ggplot(aes(x=V_comp)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

@@

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_free, y=V_osc, color=errors)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=N, y=sort(errors))) +
  ylim(0, 0.030) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=N, y=sort(delta_variances))) +
  geom_point() + 
  ylim(-0.030, 0.030) +
  geom_hline(aes(yintercept=0), color="black", alpha=0.6) +
  theme_classic()
```

```{r, fig.width=1.5, fig.height=1}
results %>% 
  # filter(errors < 0.6, coincidence_count > 0) %>%
  ggplot(aes(x=V_comp, y=normalize(delta_variances))) +
  geom_point(color="red", alpha=0.5) + 
  xlab("Vc (mvolt)") +
  ylab("Rel. scores (AU)") +
  geom_point(aes(x=V_comp, y=normalize(errors)), color="purple") + 
  theme_classic()
```

>>>>

```{r, message=FALSE}
name1 <- "../data/exp48_d-0.2e-3_f4_r1.csv"
name2 <- "../data/exp48_d-0.2e-3_f4_r100.csv"

results1 <- read_csv(paste(name1, sep=""))
results2 <- read_csv(paste(name2, sep=""))

results1 %>%
  mutate(rank = rep("1", nrow(results1))) %>% filter(n_spikes > 0) -> results1
results2 %>%
  mutate(rank = rep("100", nrow(results2))) %>% filter(n_spikes > 0) -> results2

results <- rbind(results1, results2)
rm(results1, results2)
```

```{r, fig.width=2.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=variances, fill=rank)) +
  geom_histogram(bins=20) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  ggplot(aes(x=errors, fill=rank)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  ggplot(aes(x=V_osc/V_b, fill=rank)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  ggplot(aes(x=V_comp/V_b, fill=rank)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

@@

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=As, y=V_osc/V_b, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=As, y=V_comp/V_b, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=V_comp/V_b, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_free/V_b, y=n_spikes, color=rank)) +
  geom_point() + 
  theme_classic()
```
```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=n_spikes, y=errors, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=n_spikes, y=variances, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_free/V_b, y=variances, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_free/V_b, y=errors, color=rank)) +
  geom_point() + 
  theme_classic()
```

### As

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=variances, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=n_spikes, color=rank)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=1.75, fig.height=1.25}
results %>% 
  filter(variances > 0, errors > 0) %>% 
  ggplot(aes(x=variances, y=errors, color=rank)) +
  geom_point() + 
  theme_classic()
```
